---
title: "Linear Models"
author: "Ford Holland"
date: "11/7/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(viridis)
library(p8105.datasets)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

Note: anova mostly for cats that you're interested in the effect of whole variable

Clean data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```

Fit a linear model

Bronx is reference category by default (alphabetical)
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

summary(fit)
# return coefficients
coef(fit)
broom::tidy(fit)
```

Presenting results
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```

## looking at factors

lm will convert characters to factors and level alphabetically
```{r}
# order factors by infrequency
nyc_airbnb = nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro),
    room_type = fct_infreq(room_type)
  )
```


re-fit the last model

```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)

# this form also exists
fit %>% 
  broom::glance()
```


## Diagnostics

The `modelr` package can be used to add residuals and fitted values to a dataframe.
```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_violin()
```


```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()
```


## Hypothesis testing

```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)
```

```{r}
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```


## Nesting

```{r}
fit_interaction = lm(price ~ boro*stars + room_type * boro, data = nyc_airbnb)
```


```{r}
fit_interaction %>% 
  broom::tidy()
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Map this instead

```{r}
nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(boro, results) %>% 
  unnest(results)
```

```{r}
nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  unnest(results)
```


```{r}
manhattan_nest_lm = nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  unnest(results)

manhattan_nest_lm %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```








